Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
added explaination of yellow bg in table

	\caption{Differences in memorability, believability, and desirability for different conditions of the trip or traveller. A green background denotes cases where there was a statistically significant difference within that condition.}

>>>>

	\caption{Differences in memorability, believability, and desirability for different conditions of the trip or traveller. A green background denotes cases where there was a statistically significant difference within that condition where $\alpha = 0.05$, and a yellow background denotes cases where $\alpha = 0.1$}
